---
title: "US Census Data"
author: "Brady Pearce and Dhiraj Khanna"
date: "17/06/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
```

## Introduction

The US Census API allows you to pull data directly into our environment using the `tidycensus` package.You can obtain your API key from [here](https://api.census.gov/data/key_signup.html). Let's start off by loading the requisite packages and our API key.

```{r}
library(tidyverse)
library(tidycensus)

census_api_key('3dfa1c229f23142d27afe30f76081e56a61f4c62')
```
There are two main functions for downloading ACS data and Census data - `get_acs()` and `get_decennial()`. Getting variables using the Census API requires knowing the variable ID - and there are thousands of variables (and thus thousands of IDs) across the different Census files. To rapidly search for variables, use the commands `load_variables()` and `View()`. You can get more help on any function by typing `?function_name` in the console. For eg. `?load_variables`

```{r}
v19 <- load_variables(2019, 'acs5', cache = TRUE)
head(v19)
```
Another way of finding variable names is to search them using [Social Explorer](https://www.socialexplorer.com/data/metadata/). Click on the appropriate survey data year and then “American Community Survey Tables”, which will take you to a list of variables with their Census IDs.

```{r}
# Bring in 2015-2019 census tract data using the Census API 
nc.tracts19 <- get_acs(geography = "tract", 
              year = 2019,
              variables = c(tpop = "B03002_001", 
                            nhwhite = "B03002_003", nhblk = "B03002_004",
                            nhasn = "B03002_006", hisp = "B03002_012",
                            medinc19 = "B19013_001", rent19  = "B25064_001",
                            houseval19 = "B25077_001", bach = "B15003_022",
                            masters = "B15003_023", prof = "B15003_024",
                            phd = "B15003_025", totcol = "B15003_001", tpop2 = "B01001_001", 
                            tpopml = "B01001_002", tpopmlt5 = "B01001_003",
                            tpopml5to9 = "B01001_004", tpopml10to14 = "B01001_005", 
                            tpopml15to17 = "B01001_006", tpopml18to19 = "B01001_007", 
                            tpopml20 = "B01001_008", tpopml21 = "B01001_009", 
                            tpopml22to24 = "B01001_010", tpopml25to29 = "B01001_011", 
                            tpopml30to34 = "B01001_012", tpopml35to39 = "B01001_013", 
                            tpopml40to44 = "B01001_014", tpopml45to49 = "B01001_015", 
                            tpopml50to54 = "B01001_016", tpopml55to59 = "B01001_017", 
                            tpopml60to61 = "B01001_018", tpopml62to64 = "B01001_019", 
                            tpopml65to66 = "B01001_020", tpopml67to69 = "B01001_021", 
                            tpopml70to74 = "B01001_022", tpopml75to79 = "B01001_023", 
                            tpopml80to85 = "B01001_024", tpopmlgt85 = "B01001_025",
                            tpopfml = "B01001_026", tpopfmlt5 = "B01001_027",
                            tpopfml5to9 = "B01001_028", tpopfml10to14 = "B01001_029", 
                            tpopfml15to17 = "B01001_030", tpopfml18to19 = "B01001_031", 
                            tpopfml20 = "B01001_032", tpopfml21 = "B01001_033", 
                            tpopfml22to24 = "B01001_034", tpopfml25to29 = "B01001_035", 
                            tpopfml30to34 = "B01001_036", tpopfml35to39 = "B01001_037", 
                            tpopfml40to44 = "B01001_038", tpopfml45to49 = "B01001_039", 
                            tpopfml50to54 = "B01001_040", tpopfml55to59 = "B01001_041", 
                            tpopfml60to61 = "B01001_042", tpopfml62to64 = "B01001_043", 
                            tpopfml65to66 = "B01001_044", tpopfml67to69 = "B01001_045", 
                            tpopfml70to74 = "B01001_046", tpopfml75to79 = "B01001_047", 
                            tpopfml80to85 = "B01001_048", tpopfmlgt85 = "B01001_049"),
              state = "NC",
              survey = "acs5",
              output = "wide",
              geometry = TRUE)

nc.tracts18 <- get_acs(geography = "tract", 
               year = 2018, 
               variables = c(tpop = "B03002_001", 
                            nhwhite = "B03002_003", nhblk = "B03002_004",
                            nhasn = "B03002_006", hisp = "B03002_012",
                            medinc18 = "B19013_001", rent18  = "B25064_001",
                            houseval18 = "B25077_001", bach = "B15003_022",
                            masters = "B15003_023", prof = "B15003_024",
                            phd = "B15003_025", totcol = "B15003_001", tpop2 = "B01001_001", 
                            tpopml = "B01001_002", tpopmlt5 = "B01001_003",
                            tpopml5to9 = "B01001_004", tpopml10to14 = "B01001_005", 
                            tpopml15to17 = "B01001_006", tpopml18to19 = "B01001_007", 
                            tpopml20 = "B01001_008", tpopml21 = "B01001_009", 
                            tpopml22to24 = "B01001_010", tpopml25to29 = "B01001_011", 
                            tpopml30to34 = "B01001_012", tpopml35to39 = "B01001_013", 
                            tpopml40to44 = "B01001_014", tpopml45to49 = "B01001_015", 
                            tpopml50to54 = "B01001_016", tpopml55to59 = "B01001_017", 
                            tpopml60to61 = "B01001_018", tpopml62to64 = "B01001_019", 
                            tpopml65to66 = "B01001_020", tpopml67to69 = "B01001_021", 
                            tpopml70to74 = "B01001_022", tpopml75to79 = "B01001_023", 
                            tpopml80to85 = "B01001_024", tpopmlgt85 = "B01001_025",
                            tpopfml = "B01001_026", tpopfmlt5 = "B01001_027",
                            tpopfml5to9 = "B01001_028", tpopfml10to14 = "B01001_029", 
                            tpopfml15to17 = "B01001_030", tpopfml18to19 = "B01001_031", 
                            tpopfml20 = "B01001_032", tpopfml21 = "B01001_033", 
                            tpopfml22to24 = "B01001_034", tpopfml25to29 = "B01001_035", 
                            tpopfml30to34 = "B01001_036", tpopfml35to39 = "B01001_037", 
                            tpopfml40to44 = "B01001_038", tpopfml45to49 = "B01001_039", 
                            tpopfml50to54 = "B01001_040", tpopfml55to59 = "B01001_041", 
                            tpopfml60to61 = "B01001_042", tpopfml62to64 = "B01001_043", 
                            tpopfml65to66 = "B01001_044", tpopfml67to69 = "B01001_045", 
                            tpopfml70to74 = "B01001_046", tpopfml75to79 = "B01001_047", 
                            tpopfml80to85 = "B01001_048", tpopfmlgt85 = "B01001_049"),
               show_call = TRUE,
               state = "NC",
               survey = "acs5",
               output="wide",
               geometry = TRUE)

nc.tracts17 <- get_acs(geography = "tract", 
               year = 2017, 
               variables = c(tpop = "B03002_001", 
                            nhwhite = "B03002_003", nhblk = "B03002_004",
                            nhasn = "B03002_006", hisp = "B03002_012",
                            medinc17 = "B19013_001", rent17  = "B25064_001",
                            houseval17 = "B25077_001", bach = "B15003_022",
                            masters = "B15003_023", prof = "B15003_024",
                            phd = "B15003_025", totcol = "B15003_001", tpop2 = "B01001_001", 
                            tpopml = "B01001_002", tpopmlt5 = "B01001_003",
                            tpopml5to9 = "B01001_004", tpopml10to14 = "B01001_005", 
                            tpopml15to17 = "B01001_006", tpopml18to19 = "B01001_007", 
                            tpopml20 = "B01001_008", tpopml21 = "B01001_009", 
                            tpopml22to24 = "B01001_010", tpopml25to29 = "B01001_011", 
                            tpopml30to34 = "B01001_012", tpopml35to39 = "B01001_013", 
                            tpopml40to44 = "B01001_014", tpopml45to49 = "B01001_015", 
                            tpopml50to54 = "B01001_016", tpopml55to59 = "B01001_017", 
                            tpopml60to61 = "B01001_018", tpopml62to64 = "B01001_019", 
                            tpopml65to66 = "B01001_020", tpopml67to69 = "B01001_021", 
                            tpopml70to74 = "B01001_022", tpopml75to79 = "B01001_023", 
                            tpopml80to85 = "B01001_024", tpopmlgt85 = "B01001_025",
                            tpopfml = "B01001_026", tpopfmlt5 = "B01001_027",
                            tpopfml5to9 = "B01001_028", tpopfml10to14 = "B01001_029", 
                            tpopfml15to17 = "B01001_030", tpopfml18to19 = "B01001_031", 
                            tpopfml20 = "B01001_032", tpopfml21 = "B01001_033", 
                            tpopfml22to24 = "B01001_034", tpopfml25to29 = "B01001_035", 
                            tpopfml30to34 = "B01001_036", tpopfml35to39 = "B01001_037", 
                            tpopfml40to44 = "B01001_038", tpopfml45to49 = "B01001_039", 
                            tpopfml50to54 = "B01001_040", tpopfml55to59 = "B01001_041", 
                            tpopfml60to61 = "B01001_042", tpopfml62to64 = "B01001_043", 
                            tpopfml65to66 = "B01001_044", tpopfml67to69 = "B01001_045", 
                            tpopfml70to74 = "B01001_046", tpopfml75to79 = "B01001_047", 
                            tpopfml80to85 = "B01001_048", tpopfmlgt85 = "B01001_049"),
               show_call = TRUE,
               state = "NC",
               survey = "acs5",
               output="wide",
               geometry = TRUE)

nc.tracts16 <- get_acs(geography = "tract", 
               year = 2016, 
               variables = c(tpop = "B03002_001", 
                            nhwhite = "B03002_003", nhblk = "B03002_004",
                            nhasn = "B03002_006", hisp = "B03002_012",
                            medinc16 = "B19013_001", rent16  = "B25064_001",
                            houseval16 = "B25077_001", bach = "B15003_022",
                            masters = "B15003_023", prof = "B15003_024",
                            phd = "B15003_025", totcol = "B15003_001", tpop2 = "B01001_001", 
                            tpopml = "B01001_002", tpopmlt5 = "B01001_003",
                            tpopml5to9 = "B01001_004", tpopml10to14 = "B01001_005", 
                            tpopml15to17 = "B01001_006", tpopml18to19 = "B01001_007", 
                            tpopml20 = "B01001_008", tpopml21 = "B01001_009", 
                            tpopml22to24 = "B01001_010", tpopml25to29 = "B01001_011", 
                            tpopml30to34 = "B01001_012", tpopml35to39 = "B01001_013", 
                            tpopml40to44 = "B01001_014", tpopml45to49 = "B01001_015", 
                            tpopml50to54 = "B01001_016", tpopml55to59 = "B01001_017", 
                            tpopml60to61 = "B01001_018", tpopml62to64 = "B01001_019", 
                            tpopml65to66 = "B01001_020", tpopml67to69 = "B01001_021", 
                            tpopml70to74 = "B01001_022", tpopml75to79 = "B01001_023", 
                            tpopml80to85 = "B01001_024", tpopmlgt85 = "B01001_025",
                            tpopfml = "B01001_026", tpopfmlt5 = "B01001_027",
                            tpopfml5to9 = "B01001_028", tpopfml10to14 = "B01001_029", 
                            tpopfml15to17 = "B01001_030", tpopfml18to19 = "B01001_031", 
                            tpopfml20 = "B01001_032", tpopfml21 = "B01001_033", 
                            tpopfml22to24 = "B01001_034", tpopfml25to29 = "B01001_035", 
                            tpopfml30to34 = "B01001_036", tpopfml35to39 = "B01001_037", 
                            tpopfml40to44 = "B01001_038", tpopfml45to49 = "B01001_039", 
                            tpopfml50to54 = "B01001_040", tpopfml55to59 = "B01001_041", 
                            tpopfml60to61 = "B01001_042", tpopfml62to64 = "B01001_043", 
                            tpopfml65to66 = "B01001_044", tpopfml67to69 = "B01001_045", 
                            tpopfml70to74 = "B01001_046", tpopfml75to79 = "B01001_047", 
                            tpopfml80to85 = "B01001_048", tpopfmlgt85 = "B01001_049"),
               show_call = TRUE,
               state = "NC",
               survey = "acs5",
               output="wide",
               geometry = TRUE)

nc.tracts15 <- get_acs(geography = "tract", 
               year = 2015, 
               variables = c(tpop = "B03002_001", 
                            nhwhite = "B03002_003", nhblk = "B03002_004",
                            nhasn = "B03002_006", hisp = "B03002_012",
                            medinc15 = "B19013_001", rent15  = "B25064_001",
                            houseval15 = "B25077_001", bach = "B15003_022",
                            masters = "B15003_023", prof = "B15003_024",
                            phd = "B15003_025", totcol = "B15003_001", tpop2 = "B01001_001", 
                            tpopml = "B01001_002", tpopmlt5 = "B01001_003",
                            tpopml5to9 = "B01001_004", tpopml10to14 = "B01001_005", 
                            tpopml15to17 = "B01001_006", tpopml18to19 = "B01001_007", 
                            tpopml20 = "B01001_008", tpopml21 = "B01001_009", 
                            tpopml22to24 = "B01001_010", tpopml25to29 = "B01001_011", 
                            tpopml30to34 = "B01001_012", tpopml35to39 = "B01001_013", 
                            tpopml40to44 = "B01001_014", tpopml45to49 = "B01001_015", 
                            tpopml50to54 = "B01001_016", tpopml55to59 = "B01001_017", 
                            tpopml60to61 = "B01001_018", tpopml62to64 = "B01001_019", 
                            tpopml65to66 = "B01001_020", tpopml67to69 = "B01001_021", 
                            tpopml70to74 = "B01001_022", tpopml75to79 = "B01001_023", 
                            tpopml80to85 = "B01001_024", tpopmlgt85 = "B01001_025",
                            tpopfml = "B01001_026", tpopfmlt5 = "B01001_027",
                            tpopfml5to9 = "B01001_028", tpopfml10to14 = "B01001_029", 
                            tpopfml15to17 = "B01001_030", tpopfml18to19 = "B01001_031", 
                            tpopfml20 = "B01001_032", tpopfml21 = "B01001_033", 
                            tpopfml22to24 = "B01001_034", tpopfml25to29 = "B01001_035", 
                            tpopfml30to34 = "B01001_036", tpopfml35to39 = "B01001_037", 
                            tpopfml40to44 = "B01001_038", tpopfml45to49 = "B01001_039", 
                            tpopfml50to54 = "B01001_040", tpopfml55to59 = "B01001_041", 
                            tpopfml60to61 = "B01001_042", tpopfml62to64 = "B01001_043", 
                            tpopfml65to66 = "B01001_044", tpopfml67to69 = "B01001_045", 
                            tpopfml70to74 = "B01001_046", tpopfml75to79 = "B01001_047", 
                            tpopfml80to85 = "B01001_048", tpopfmlgt85 = "B01001_049"),
               show_call = TRUE,
               state = "NC",
               survey = "acs5",
               output="wide",
               geometry = TRUE)
                      
```

```{r}
library(sf)
library(tmap)
library(rmapshaper)
library(tigris)4
# Make the data tidy, calculate and keep essential vars. 
nc.tracts19 <- nc.tracts19 %>% 
  rename_with(~ sub("E$", "", .x), everything()) %>%
  mutate(pnhwhite19 = 100*(nhwhite/tpop), pnhasn19 = 100*(nhasn/tpop), 
        pnhblk19 = 100*(nhblk/tpop), phisp19 = 100*(hisp/tpop), 
        pcol19 = 100*(bach+masters+prof+phd)/totcol) %>%
  select(c(GEOID,tpop, pnhwhite19, pnhasn19, pnhblk19, phisp19,
           nhwhite, nhasn, nhblk, hisp,
           medinc19, rent19, houseval19, pcol19, tpop2, 
                            tpopml, tpopmlt5,
                            tpopml5to9, tpopml10to14, 
                            tpopml15to17, tpopml18to19, 
                            tpopml20, tpopml21, 
                            tpopml22to24, tpopml25to29, 
                            tpopml30to34, tpopml35to39, 
                            tpopml40to44, tpopml45to49, 
                            tpopml50to54, tpopml55to59, 
                            tpopml60to61, tpopml62to64, 
                            tpopml65to66, tpopml67to69, 
                            tpopml70to74, tpopml75to79, 
                            tpopml80to85, tpopmlgt85,
                            tpopfml, tpopfmlt5,
                            tpopfml5to9, tpopfml10to14, 
                            tpopfml15to17, tpopfml18to19, 
                            tpopfml20, tpopfml21, 
                            tpopfml22to24, tpopfml25to29, 
                            tpopfml30to34, tpopfml35to39, 
                            tpopfml40to44, tpopfml45to49, 
                            tpopfml50to54, tpopfml55to59, 
                            tpopfml60to61, tpopfml62to64, 
                            tpopfml65to66, tpopfml67to69, 
                            tpopfml70to74, tpopfml75to79, 
                            tpopfml80to85, tpopfmlgt85))  

nc.tracts18 <- nc.tracts18 %>% 
  rename_with(~ sub("E$", "", .x), everything()) %>%
  mutate(pnhwhite18 = 100*(nhwhite/tpop), pnhasn18 = 100*(nhasn/tpop), 
        pnhblk18 = 100*(nhblk/tpop), phisp18 = 100*(hisp/tpop), 
        pcol18 = 100*(bach+masters+prof+phd)/totcol) %>%
  select(c(GEOID,tpop, pnhwhite18, pnhasn18, pnhblk18, phisp18,
           nhwhite, nhasn, nhblk, hisp,
           medinc18, rent18, houseval18, pcol18,tpop2, 
                            tpopml, tpopmlt5,
                            tpopml5to9, tpopml10to14, 
                            tpopml15to17, tpopml18to19, 
                            tpopml20, tpopml21, 
                            tpopml22to24, tpopml25to29, 
                            tpopml30to34, tpopml35to39, 
                            tpopml40to44, tpopml45to49, 
                            tpopml50to54, tpopml55to59, 
                            tpopml60to61, tpopml62to64, 
                            tpopml65to66, tpopml67to69, 
                            tpopml70to74, tpopml75to79, 
                            tpopml80to85, tpopmlgt85,
                            tpopfml, tpopfmlt5,
                            tpopfml5to9, tpopfml10to14, 
                            tpopfml15to17, tpopfml18to19, 
                            tpopfml20, tpopfml21, 
                            tpopfml22to24, tpopfml25to29, 
                            tpopfml30to34, tpopfml35to39, 
                            tpopfml40to44, tpopfml45to49, 
                            tpopfml50to54, tpopfml55to59, 
                            tpopfml60to61, tpopfml62to64, 
                            tpopfml65to66, tpopfml67to69, 
                            tpopfml70to74, tpopfml75to79, 
                            tpopfml80to85, tpopfmlgt85))  

nc.tracts17 <- nc.tracts17 %>% 
  rename_with(~ sub("E$", "", .x), everything()) %>%
  mutate(pnhwhite17 = 100*(nhwhite/tpop), pnhasn17 = 100*(nhasn/tpop), 
        pnhblk17 = 100*(nhblk/tpop), phisp17 = 100*(hisp/tpop), 
        pcol17 = 100*(bach+masters+prof+phd)/totcol) %>%
  select(c(GEOID,tpop, pnhwhite17, pnhasn17, pnhblk17, phisp17,
           nhwhite, nhasn, nhblk, hisp,
           medinc17, rent17, houseval17, pcol17,tpop2, 
                            tpopml, tpopmlt5,
                            tpopml5to9, tpopml10to14, 
                            tpopml15to17, tpopml18to19, 
                            tpopml20, tpopml21, 
                            tpopml22to24, tpopml25to29, 
                            tpopml30to34, tpopml35to39, 
                            tpopml40to44, tpopml45to49, 
                            tpopml50to54, tpopml55to59, 
                            tpopml60to61, tpopml62to64, 
                            tpopml65to66, tpopml67to69, 
                            tpopml70to74, tpopml75to79, 
                            tpopml80to85, tpopmlgt85,
                            tpopfml, tpopfmlt5,
                            tpopfml5to9, tpopfml10to14, 
                            tpopfml15to17, tpopfml18to19, 
                            tpopfml20, tpopfml21, 
                            tpopfml22to24, tpopfml25to29, 
                            tpopfml30to34, tpopfml35to39, 
                            tpopfml40to44, tpopfml45to49, 
                            tpopfml50to54, tpopfml55to59, 
                            tpopfml60to61, tpopfml62to64, 
                            tpopfml65to66, tpopfml67to69, 
                            tpopfml70to74, tpopfml75to79, 
                            tpopfml80to85, tpopfmlgt85)) 

nc.tracts16 <- nc.tracts16 %>% 
  rename_with(~ sub("E$", "", .x), everything()) %>%
  mutate(pnhwhite16 = 100*(nhwhite/tpop), pnhasn16 = 100*(nhasn/tpop), 
        pnhblk16 = 100*(nhblk/tpop), phisp16 = 100*(hisp/tpop), 
        pcol16 = 100*(bach+masters+prof+phd)/totcol) %>%
  select(c(GEOID,tpop, pnhwhite16, pnhasn16, pnhblk16, phisp16,
           nhwhite, nhasn, nhblk, hisp,
           medinc16, rent16, houseval16, pcol16, tpop2, 
                            tpopml, tpopmlt5,
                            tpopml5to9, tpopml10to14, 
                            tpopml15to17, tpopml18to19, 
                            tpopml20, tpopml21, 
                            tpopml22to24, tpopml25to29, 
                            tpopml30to34, tpopml35to39, 
                            tpopml40to44, tpopml45to49, 
                            tpopml50to54, tpopml55to59, 
                            tpopml60to61, tpopml62to64, 
                            tpopml65to66, tpopml67to69, 
                            tpopml70to74, tpopml75to79, 
                            tpopml80to85, tpopmlgt85,
                            tpopfml, tpopfmlt5,
                            tpopfml5to9, tpopfml10to14, 
                            tpopfml15to17, tpopfml18to19, 
                            tpopfml20, tpopfml21, 
                            tpopfml22to24, tpopfml25to29, 
                            tpopfml30to34, tpopfml35to39, 
                            tpopfml40to44, tpopfml45to49, 
                            tpopfml50to54, tpopfml55to59, 
                            tpopfml60to61, tpopfml62to64, 
                            tpopfml65to66, tpopfml67to69, 
                            tpopfml70to74, tpopfml75to79, 
                            tpopfml80to85, tpopfmlgt85))  

nc.tracts15 <- nc.tracts15 %>% 
  rename_with(~ sub("E$", "", .x), everything()) %>%
  mutate(pnhwhite15 = 100*(nhwhite/tpop), pnhasn15 = 100*(nhasn/tpop), 
        pnhblk15 = 100*(nhblk/tpop), phisp15 = 100*(hisp/tpop), 
        pcol15 = 100*(bach+masters+prof+phd)/totcol) %>%
  select(c(GEOID,tpop, pnhwhite15, pnhasn15, pnhblk15, phisp15,
           nhwhite, nhasn, nhblk, hisp,
           medinc15, rent15, houseval15, pcol15, tpop2, 
                            tpopml, tpopmlt5,
                            tpopml5to9, tpopml10to14, 
                            tpopml15to17, tpopml18to19, 
                            tpopml20, tpopml21, 
                            tpopml22to24, tpopml25to29, 
                            tpopml30to34, tpopml35to39, 
                            tpopml40to44, tpopml45to49, 
                            tpopml50to54, tpopml55to59, 
                            tpopml60to61, tpopml62to64, 
                            tpopml65to66, tpopml67to69, 
                            tpopml70to74, tpopml75to79, 
                            tpopml80to85, tpopmlgt85,
                            tpopfml, tpopfmlt5,
                            tpopfml5to9, tpopfml10to14, 
                            tpopfml15to17, tpopfml18to19, 
                            tpopfml20, tpopfml21, 
                            tpopfml22to24, tpopfml25to29, 
                            tpopfml30to34, tpopfml35to39, 
                            tpopfml40to44, tpopfml45to49, 
                            tpopfml50to54, tpopfml55to59, 
                            tpopfml60to61, tpopfml62to64, 
                            tpopfml65to66, tpopfml67to69, 
                            tpopfml70to74, tpopfml75to79, 
                            tpopfml80to85, tpopfmlgt85))  

# Bring in city boundaries
pl <- tigris::places(state = "NC", year = 2019, cb = TRUE)


# Keep four large cities in NC
large_cities <- c('Charlotte', 'Fayetteville', 'Raleigh', 'Winston-Salem')
large.cities <- pl %>% filter(NAME %in% large_cities)
#Keep tracts in large cities 

large.tracts19 <- ms_clip(target = nc.tracts19, clip = large.cities, remove_slivers = TRUE)
sf::sf_use_s2(FALSE)
large.tracts <- large.tracts %>%
                st_join(large.cities, left=FALSE)

large.tracts18 <- ms_clip(target = nc.tracts18, clip = large.cities, remove_slivers = TRUE)
sf::sf_use_s2(FALSE)
large.tracts <- large.tracts %>%
                st_join(large.cities, left=FALSE)

large.tracts17 <- ms_clip(target = nc.tracts17, clip = large.cities, remove_slivers = TRUE)
sf::sf_use_s2(FALSE)
large.tracts <- large.tracts %>%
                st_join(large.cities, left=FALSE)

large.tracts16 <- ms_clip(target = nc.tracts16, clip = large.cities, remove_slivers = TRUE)
sf::sf_use_s2(FALSE)
large.tracts <- large.tracts %>%
                st_join(large.cities, left=FALSE)

large.tracts15 <- ms_clip(target = nc.tracts15, clip = large.cities, remove_slivers = TRUE)
sf::sf_use_s2(FALSE)
large.tracts <- large.tracts %>%
                st_join(large.cities, left=FALSE)



```
```{r}
df_19 <- as.data.frame(large.tracts19) %>% select(-geometry)
df_18 <- as.data.frame(large.tracts18) %>% select(-geometry)
df_17 <- as.data.frame(large.tracts17) %>% select(-geometry)
df_16 <- as.data.frame(large.tracts16) %>% select(-geometry)
df_15 <- as.data.frame(large.tracts15) %>% select(-geometry)



```

```{r}
write.csv(df_19, "C:/Users/Brady Pearce/Documents/Springboard/df_19.csv")
write.csv(df_18, "C:/Users/Brady Pearce/Documents/Springboard/df_18.csv")
write.csv(df_17, "C:/Users/Brady Pearce/Documents/Springboard/df_17.csv")
write.csv(df_16, "C:/Users/Brady Pearce/Documents/Springboard/df_16.csv")
write.csv(df_15, "C:/Users/Brady Pearce/Documents/Springboard/df_15.csv")
```


```{r}
large.tracts %>%
  filter(NAME == "Raleigh") %>%
  tm_shape(unit = "mi") +
    tm_polygons(col = "phisp19", style = "quantile",palette = "Reds", 
              border.alpha = 0, title = "") +
    tm_scale_bar(breaks = c(0, 1, 2), text.size = 0.75, position = c("right", "bottom")) + tm_layout(main.title = "Percent Hispanic in Raleigh City Tracts 2019", main.title.size = 0.9, frame = FALSE)

```
```{r}
large.tracts %>%
  filter(NAME == "Raleigh") %>%
tm_shape(unit = "mi") +
  tm_polygons(col = "pnhwhite19", style = "quantile",palette = "Reds", 
              border.alpha = 0, title = "") +
  tm_scale_bar(breaks = c(0, 1, 2), text.size = 0.75, position = c("right", "bottom")) +  tm_layout(main.title = "Percent White in Raleigh City Tracts", main.title.size = 0.9,
            frame = FALSE)
```
Download ACS data for 2010

```{r}
# Bring in 2006-2010 census tract data using the Census API 
nc.tracts10 <- get_acs(geography = "tract", 
              year = 2010,
              variables = c(medinc10 = "B19013_001", rent10  = "B25064_001",
                            houseval10 = "B25077_001", bachm = "B15002_015",
                            mastersm = "B15002_016", profm = "B15002_017",
                            phdm = "B15002_018", bachf = "B15002_032",
                            mastersf = "B15002_033", proff = "B15002_034",
                            phdf = "B15002_035", totcol = "B15002_001"),
              state = "NC",
              survey = "acs5",
              output = "wide")

# Make the data tidy, calculate and keep essential vars. 
nc.tracts10 <- nc.tracts10 %>% 
  rename_with(~ sub("E$", "", .x), everything()) %>%
  mutate(pcol10 = 100*(bachm+mastersm+profm+phdm+bachf+mastersf+proff+phdf)/totcol) %>%
  select(c(GEOID,medinc10, rent10, houseval10, pcol10)) 
```


```{r}
# Bring in census tract data using the Census API 
nc.places10 <- get_acs(geography = "place", 
              year = 2010,
              variables = c(medincc10 = "B19013_001", rentc10  = "B25064_001",
                            housevalc10 = "B25077_001", bachm = "B15002_015",
                            mastersm = "B15002_016", profm = "B15002_017",
                            phdm = "B15002_018", bachf = "B15002_032",
                            mastersf = "B15002_033", proff = "B15002_034",
                            phdf = "B15002_035", totcol = "B15002_001"),
              state = "NC",
              survey = "acs5",
              output = "wide")

# Make the data tidy, calculate and keep essential vars. Also take out zero population tracts
nc.places10 <- nc.places10 %>% 
  rename_with(~ sub("E$", "", .x), everything()) %>%
  mutate(pcolc10 = 100*(bachm+mastersm+profm+phdm+bachf+mastersf+proff+phdf)/totcol) %>%
  select(c(GEOID,medincc10, rentc10, housevalc10, pcolc10)) 
```

```{r}
# Bring in census tract data using the Census API 
nc.places19 <- get_acs(geography = "place", 
              year = 2019,
              variables = c(medincc19 = "B19013_001", rentc19  = "B25064_001",
                            housevalc19 = "B25077_001", bachc = "B15003_022",
                            mastersc = "B15003_023", profc = "B15003_024",
                            phdc = "B15003_025", totcolc = "B15003_001"),
              state = "NC",
              survey = "acs5",
              output = "wide")

# Make the data tidy, calculate and keep essential vars. Also take out zero population tracts
nc.places19 <- nc.places19 %>% 
  rename_with(~ sub("E$", "", .x), everything()) %>%
  mutate(pcolc19 = 100*(bachc+mastersc+profc+phdc)/totcolc) %>%
  select(c(GEOID,medincc19, rentc19, housevalc19, pcolc19)) 
```


```{r}
charlotte.tracts <- large.tracts %>%
            filter(NAME == "Charlotte")


charlotte.tracts <- charlotte.tracts %>%
            left_join(nc.tracts10, by = c("GEOID.x" = "GEOID"))


charlotte.tracts <- charlotte.tracts %>%
            left_join(nc.places10, by = c("GEOID.y" = "GEOID")) %>%
            left_join(nc.places19, by = c("GEOID.y" = "GEOID")) 
```

